\documentclass[12pt,a4paper]{article}
\usepackage{amsmath}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{setspace}
\onehalfspacing
\usepackage[danish]{babel}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{pst-tree}
\usepackage{tikz}
\usetikzlibrary{trees}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage[top=2.5cm, bottom=2.5cm, left=2.5cm, right=2.5cm]{geometry}
\usepackage{enumerate} 
\usepackage{amssymb}
\usepackage{csquotes}
\usepackage{fancyhdr}
\usepackage{times}
\usepackage{gauss}
\usepackage{fancyhdr}
\usepackage[bottom]{footmisc}
\pagestyle{fancy}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{lscape}
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
\node[shape=circle,draw,inner sep=2pt] (char) {#1};}}
\DeclareMathSizes{12}{12}{10}{10}
\interfootnotelinepenalty=10000
\usepackage{dsfont}
\usepackage{mathtools}
\usepackage{graphics}
\usepackage[danish]{babel} 
\usepackage{graphicx}
\usepackage{multirow, booktabs}
\usepackage[final]{pdfpages}
\usepackage{hyperref}
\pagenumbering{gobble}

\lhead{}
\rhead{}
\chead{}

\usepackage{graphicx}

\begin{document}

\title{Predicting Evaluation Prices of Danish Real Estate Property} 
\author{Exam-numbers 115, 144, 146, 204}
\maketitle
\section*{}
The intention of this project is to predict which features are most relevant for evaluation of real estate properties in Denmark. Two prediction models will be used, one with a classification output by price-intervals. The second model with a continuous output. Data will be scraped from \href{https://www.boliga.dk}{boliga.dk}, \href{https://www.hvorlangterder.dk}{hvorlangterder.dk}, \href{https://statistik.politi.dk/QvAJAXZfc/opendoc.htm?document=QlikApplication%2F2999_Public\%2FPublic_IndsatsResultater.qvw}{statistik.politi.dk},
 \href{https://www.dst.dk/da/Statistik/emner/befolkning-og-valg}{Danmarks Statistik}.
The data from \href{https://www.boliga.dk}{boliga.dk} and \href{https://www.hvorlangterder.dk}{hvorlangterder.dk} are undoubtedly essential to the model. Whereas the data scraped from \href{https://statistik.politi.dk/QvAJAXZfc/opendoc.htm?document=QlikApplication%2F2999_Public\%2FPublic_IndsatsResultater.qvw}{statistik.politi.dk} 
and \href{https://statistikbanken.dk/statbank5a/default.asp?w=1280}{Statistikbanken} contributes with potential to include socio-economic factors.\newline
The model will take variation in pricing caused by geographical matters, as well as differences in types of housing into account.
Machine learning will be applied, for the purpose of prediction of prices. Because of the large amount of terms and corresponding interaction-terms in the prediction-model, regularization by the Lasso-feature will be used. 

\end{document}
